---
title: "P8105 Homework 5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
```


## Problem 1: Longitudinal Study 

#### Combine separate files into one dataset

```{r longstudy_df, message = FALSE}
# Create a dataframe containing file names.
longstudy_filenames = 
  tibble(subject = list.files("data")) %>% 
  mutate(subject = str_c("./data/", subject))

# Iterate over filenames and read in data as one dataframe
longstudy_df = 
  longstudy_filenames %>% 
  mutate(subject_data = map(.x = subject, ~read_csv(.x))) %>% 
  unnest()
```

#### Clean and tidy dataset

```{r longstudy_df1}
# Clean and tidy dataset
# Separate filename to only contain subjectID
# Group subjectIDs by control or experimental arm
longstudy_df = longstudy_df %>% 
  separate(subject, into = c("remove1", "subjectID"), sep = "a/") %>% 
  separate(subjectID, into = c("subjectID", "remove2"), sep = ".c") %>%
  mutate(subject_ID = subjectID) %>% 
  separate(subjectID, into = c("subject_group", "subject_ID2"), sep = "_") %>% 
  select(subject_group, subject_ID, week_1:week_8) %>% 
  mutate(subject_group = recode(subject_group, 
                                con = "control", 
                                exp = "experimental"))

# Tidy weekly observations by gathering week variables into one variable
longstudy_df = longstudy_df %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  separate(week, into = c("remove1", "week"), sep = "_") %>% 
  select(subject_group, subject_ID, week, value) %>% 
  mutate(week = as.numeric(week))
  
longstudy_df
```

#### Spaghetti plot: Observations over time

```{r plot1}
# Create a spaghetti plot showing observations of each subject over time
# Group by experimental and control arms
longstudy_df %>% 
  ggplot(aes(x = week, y = value, group = subject_ID, color = subject_group)) + 
  geom_line() + 
  labs(
    title = "Observations of control vs. experimental groups over weeks", 
    x = "Week", 
    y = "Value"
  ) + 
  theme_bw()
```
  
Based off of this plot, the experimental group increases in values over the 8 week period. The control group, on the other hand, does not change much over the 8 week period.    


## Problem 2: Washington Post Homicide Dataset

#### Load and describe dataset

```{r homicide_df, message = FALSE}
# Pull dataset from web and convert it to readable format in R
# Create city_state variable that combines city and state
homicide_df = read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")) %>% 
  unite(city_state, city:state, sep = ", ")

```
  
The Washington Post homicide dataset contains `r nrow(homicide_df)` observations. Each observation describes an individual homicide case across the United States. There are `r ncol(homicide_df)` variables in this dataset. Several of these variable describe the victim of the homicides including their names, age, and other demographic descriptions. For example, `r 100 * round(nrow(filter(homicide_df, homicide_df$victim_sex == "Male"))/nrow(homicide_df), digits = 4)`% of victims were male. A table below further describe the race of homicide victims. Other variables describe the location including latitude and longitude. The city and state variables were combined into one variable. This dataset contains information from `r nrow(distinct(homicide_df, homicide_df$city_state))` cities in the US. Finally, the disposition variable describes whether or not the homicide case has been left open or close and whether these cases ended with or without an arrest.

```{r summary_tables}
# Summarize proportions of victim race
homicide_df %>% 
  group_by(victim_race) %>% 
  summarize(n = n()) %>% 
  mutate(proportion = round(n / nrow(homicide_df), digits = 4)) %>% 
  knitr::kable()

# Summarize proportions of dispositions
homicide_df %>% 
  group_by(disposition) %>% 
  summarize(n = n()) %>% 
  mutate(proportion = round(n / nrow(homicide_df), digits = 4)) %>% 
  knitr::kable()
```


#### Summarize the total number of homicides and unsolved homicides by city.

```{r}
# Summarize total number of homicides by city
total_hom = homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total_homicides = n())

# Summarize total number of unsolved homicides by city
unsolved_hom = homicide_df %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(unsolved_homicides = n())

# Combine summaries into one dataframe
homicide_count = inner_join(total_hom, unsolved_hom, by = "city_state")
homicide_count
```

#### Perform prop.test on Baltimore, MD homicide counts

```{r}
# Filter homicide_count dataset to only include Baltimore, MD
sample = 
  homicide_count %>% 
  filter(city_state == "Baltimore, MD")

# Perform proportion test on Baltimore, MD
prop.test(sample$unsolved_homicides, sample$total_homicides) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

#### Create proportion test function

```{r prop_test_function}
prop_test = function(unsolved_homicides, total_homicides){
  
  prop = prop.test(unsolved_homicides, total_homicides)
  
  broom::tidy(prop) %>% 
    select(estimate, conf.low, conf.high)
}
```

#### Apply prop.test across each US city

```{r}
homicide_count = homicide_count %>% 
  mutate(homicide_prop = 
  map2(.x = homicide_count$unsolved_homicides, .y = homicide_count$total_homicides, 
      ~prop_test(.x, .y))) %>% 
  unnest()
```

#### Plot estimated proportions of unsolved homicides in each US city

```{r}
homicide_count %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(
    title = "Estimated proportion of unsolved homicides in US cities",
    x = "Location (City, State)",
    y = "Estimated Proportion"
  ) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

The city with the lowest proportion of unsolved homicide cases is Richmond, VA while the city with the highest proportion of unsolved homicide cases is Chicago, Il.