---
title: "P8105 Homework 5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
```


## Problem 1: Longitudinal Study 

#### Combine separate files into one dataset

```{r longstudy_df, message = FALSE}
# Create a dataframe containing file names.
# Input for extracting file data
longstudy_filenames = 
  tibble(subject = list.files("data")) %>% 
  mutate(subject = str_c("./data/", subject))

# Iterate over filenames and read in data into one dataframe
longstudy_df = 
  longstudy_filenames %>% 
  mutate(subject_data = map(.x = subject, ~read_csv(.x))) %>% 
  unnest()
```

#### Clean and tidy dataset

```{r longstudy_df1}
# Clean and tidy dataset
# Separate filename in subject to only contain subjectID
# Group subjectIDs by individuals administered control or experimental arm
longstudy_df = longstudy_df %>% 
  separate(subject, into = c("remove1", "subjectID"), sep = "a/") %>% 
  separate(subjectID, into = c("subjectID", "remove2"), sep = ".c") %>%
  mutate(subject_ID = subjectID) %>% 
  separate(subjectID, into = c("subject_group", "subject_ID2"), sep = "_") %>% 
  select(subject_group, subject_ID, week_1:week_8) %>% 
  mutate(subject_group = recode(subject_group, 
                                con = "control", 
                                exp = "experimental"))

# Tidy weekly observations by gathering weekly observations
longstudy_df = longstudy_df %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  separate(week, into = c("remove1", "week"), sep = "_") %>% 
  select(subject_group, subject_ID, week, value) %>% 
  mutate(week = as.numeric(week))
  
longstudy_df
```

#### Spaghetti plot: Observations over time

```{r plot1}
# Create a spaghetti plot showing observations of each subject over time
longstudy_df %>% 
  ggplot(aes(x = week, y = value, group = subject_ID, color = subject_group)) + 
  geom_line() + 
  labs(
    title = "Observations of control vs. experimental groups over weeks", 
    x = "Week", 
    y = "Value"
  ) + 
  theme_bw()
```


## Problem 2: Washington Post Homicide Dataset

```{r homicide_df, message = FALSE}
# Pull dataset from web and convert it to readable format in R
# Create city_state variable that combines city and state
homicide_df = read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")) %>% 
    unite(city_state, city:state, sep = ", ") 

```

```{r}
# Summarize total number of homicides by city
total_hom = homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total_homicides = n())

# Summarize total number of unsolved homicides by city
unsolved_hom = homicide_df %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(unsolved_homicides = n())

homicide_count = inner_join(total_hom, unsolved_hom, by = "city_state")
homicide_count
```

#### Perform prop.test on Baltimore, MD homicide counts

```{r}
# Filter homocide_count dataset to only include Baltimore, MD
sample = 
  homicide_count %>% 
  filter(city_state == "Baltimore, MD")

# Perform proportion test on Baltimore, MD
prop.test(sample$unsolved_homicides, sample$total_homicides) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

#### Create proportion test function

```{r prop_test_function}
prop_test = function(unsolved_homicides, total_homicides){
  
  prop = prop.test(unsolved_homicides, total_homicides)
  
  broom::tidy(prop) %>% 
    select(estimate, conf.low, conf.high)
}
```

#### Apply prop.test across each US city

```{r}
homicide_count = homicide_count %>% 
  mutate(homicide_prop = 
  map2(.x = homicide_count$unsolved_homicides, .y = homicide_count$total_homicides, 
      ~prop_test(.x, .y))) %>% 
  unnest()
```

#### Plot estimated proportions of unsolved homicides in each US city

```{r}
homicide_count %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(
    title = "Estimated proportion of unsolved homicides in US cities",
    x = "Location (City, State)",
    y = "Estimated Proportion"
  ) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

